### 2019-08-07 README.Rmd
update readme

[![Travis build status](https://travis-ci.org/kevinykuo/deeptriangle.svg?branch=master)](https://travis-ci.org/kevinykuo/deeptriangle)

@@

``` r
devtools::install_github("kevinykuo/deeptriangle")
```

You will also need the [insurance](https://github.com/kevinykuo/insurance) package, which can be installed with

```r
devtools::install_github("kevinykuo/insurance")
```

@@

```{r, message = FALSE}
predictions <- feather::read_feather("output/predictions.feather")

model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(read_csv("analysis/automl_results.csv")) %>%
  gather(metric, value, mape, rmspe)

>>>>

[![Travis build status](https://travis-ci.org/kasaai/deeptriangle.svg?branch=master)](https://travis-ci.org/kasaai/deeptriangle)

@@

``` r
devtools::install_github("kasaai/deeptriangle")
```

You will also need the [insurance](https://github.com/kasaai/insurance) package, which can be installed with

```r
devtools::install_github("kasaai/insurance")
```

@@

```{r, message = FALSE}
predictions <- feather::read_feather("datasets/predictions.feather")

model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(read_csv("datasets/automl_results.csv")) %>%
  gather(metric, value, mape, rmspe)
